Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
moved O'Dorney mention from section3 to intro

@@

In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical? I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise. Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$. \todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points. \todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper. Can you state this more precisely, or possibly just remove it.}

>>>>

\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical? I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise. Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$. \todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points. \todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper. Can you state this more precisely, or possibly just remove it.}

@@

Previously discussed O'Dorney's result and our improvement when restricting to effective. Moved to Intro.
\todo{new transition}
